### 2020-05-15 intro.tex
added discussion of parameterization to intro

  \item \textbf{Compositionality}: 
  Graphite does not provide any way to {enter subexpressions within a palette}.
  At best, palettes can contain text boxes, but expressions entered into these text boxes 
  do not have any editor support (which creates many problems, one of which is that they cannot themselves be generated by palettes). 
  This implies that palettes can only reasonably generate {closed expressions}. 
  For example, in Figure~\ref{fig:color}(a), the color palette
  is useful only for generating simple color constants. 
  By contrast, livelits have first-class support for subexpressions, which we call \emph{splices} (following
  the terminology of \citet{TLMs} who developed reasoning principles for splicing in a purely textual setting).
  Fig.~\ref{fig:color}(b) demonstrates splicing: the client is able to define a variable, \li{grayLevel}, 
  to capture the relationship between the red, green, and blue components.
  The client is also able to use a slider inline in the splice governing 
  the alpha (A) component.
  \item \textbf{Liveness}: Graphite's palettes do not have 
  access to the run-time environment. By contrast, livelits can evaluate splices
  and therefore provide feedback related to the run-time behavior of the expression being generated. 
  For example, in Fig.~\ref{fig:color}(b), the color that is displayed is determined by evaluating the RGBA 
  component splices to numeric values.
  Evaluation occurs in a run-time environment (i.e. closure) determined by 
  leaving the hole being filled by the livelit temporarily unfilled and then evaluating
  using a two-phased variation on the semantics for incomplete programs developed by \citet{HazelnutLive}. 
  We will see more sophisticated examples later in the paper, including a livelit 
  that appears inside a function that is called multiple times, leading to multiple closures for the client 
  select from.
  \item \textbf{Parameterization}: 
    \cyrus{... this would be really nice to include + demonstrate with slider bounds and later data flow + 
    we need it to do anything non-trivial with hygiene 
    ...}
\end{enumerate}
\clearpage

>>>>

  \item \textbf{Compositionality}: 
  Graphite does not provide any way to {enter subexpressions within a palette}.
  At best, palettes can contain text boxes, but expressions entered into these text boxes 
  do not have any editor support (which creates many problems, one of which is that they cannot themselves be generated by palettes). 
  This implies that palettes can only reasonably generate {closed expressions}. 
  For example, in Figure~\ref{fig:color}(a), the color palette
  is useful only for generating simple color constants. 
  By contrast, livelits have first-class support for subexpressions, which we call \emph{splices} (following
  the terminology of \citet{TLMs} who developed reasoning principles for splicing in a purely textual setting).
  Fig.~\ref{fig:color}(b) demonstrates splicing: the client is able to define a variable, \li{grayLevel}, 
  to capture the relationship between the red, green, and blue components.
  The client is also able to use a slider inline in the splice governing 
  the alpha (A) component.
  \item \textbf{Liveness}: Graphite's palettes do not have 
  access to the run-time environment. By contrast, livelits can evaluate splices
  and therefore provide feedback related to the run-time behavior of the expression being generated. 
  For example, in Fig.~\ref{fig:color}(b), the color that is displayed is determined by evaluating the RGBA 
  component splices to numeric values.
  Evaluation occurs in a run-time environment (i.e. closure) determined by 
  leaving the hole being filled by the livelit temporarily unfilled and then evaluating
  using a two-phased variation on the semantics for incomplete programs developed by \citet{HazelnutLive}. 
  We will see more sophisticated examples later in the paper, including a livelit 
  that appears inside a function that is called multiple times, leading to multiple closures for the client 
  select from.
  \item \textbf{Parameterization}: Finally, it is possible to define parameterized families of livelits. 
  For example, the \li{\$slider} livelit in Fig.~\ref{fig:color}(b) is parameterized by the lower and upper bound. 
  Parameters behave like splices, differing in that (1) livelits support partial parameter application, and (2) 
  livelit applications can be abbreviated. For example, it is possible to define a livelit named \li{\$percentage} 
  that operates as a \li{\$slider} from \li{0} to \li{100} by abbreviation:
  \begin{lstlisting}[numbers=none]
  let livelit $percentage = $slider(0, 100) in ...
  \end{lstlisting}
  Parameterization also underlies the hygiene mechanism, as we will discuss in Sec. 4\todo{sec}{}.
\end{enumerate}
\clearpage

### 2020-05-15 livelits-paper.tex
added discussion of parameterization to intro

\usepackage{listings}%
\lstloadlanguages{ML}
\lstset{tabsize=2, 
basicstyle=\footnotesize\ttfamily, 
% keywordstyle=\sffamily,
commentstyle=\itshape\ttfamily\color{gray}, 
stringstyle=\ttfamily\color{purple},
mathescape=false,escapechar=\#,
numbers=left, numberstyle=\scriptsize\color{gray}\ttfamily, language=ML, showspaces=false,showstringspaces=false,xleftmargin=15pt, 
morekeywords={string, float, int, Int, Float, String},
classoffset=0,belowskip=\smallskipamount, aboveskip=\smallskipamount,
moredelim=**[is][\color{red}]{SSTR}{ESTR}
}
\newcommand{\li}[1]{\lstinline[basicstyle=\ttfamily\fontsize{9pt}{1em}\selectfont]{#1}}
\newcommand{\lismall}[1]{\lstinline[basicstyle=\ttfamily\fontsize{9pt}{1em}\selectfont]{#1}}

@@

\author{David Moon}
% \authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  % \position{Position1}
  % \department{Department1}              %% \department is recommended
  \institution{University of Colorado Boulder}            %% \institution is required
  % \streetaddress{Street1 Address1}
  % \city{City1}
  % \state{State1}
  % \postcode{Post-Code1}
  % \country{Country1}
}
\email{domo9239@colorado.edu}          %% \email is recommended

>>>>

\usepackage{listings}%
\lstloadlanguages{ML}
\lstset{tabsize=2, 
basicstyle=\footnotesize\ttfamily, 
% keywordstyle=\sffamily,
commentstyle=\itshape\ttfamily\color{gray}, 
stringstyle=\ttfamily\color{purple},
mathescape=false,escapechar=\#,
numbers=left, numberstyle=\scriptsize\color{gray}\ttfamily, language=ML, showspaces=false,showstringspaces=false,xleftmargin=15pt, 
morekeywords={string, float, int, Int, Float, String, livelit},
classoffset=0,belowskip=\smallskipamount, aboveskip=\smallskipamount,
moredelim=**[is][\color{red}]{SSTR}{ESTR}
}
\newcommand{\li}[1]{\lstinline[basicstyle=\ttfamily\fontsize{9pt}{1em}\selectfont]{#1}}
\newcommand{\lismall}[1]{\lstinline[basicstyle=\ttfamily\fontsize{9pt}{1em}\selectfont]{#1}}

@@

\author{David Moon}
% \authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  % \position{Position1}
  % \department{Department1}              %% \department is recommended
  \institution{University of Michigan}            %% \institution is required
  % \streetaddress{Street1 Address1}
  % \city{City1}
  % \state{State1}
  % \postcode{Post-Code1}
  % \country{Country1}
}
\email{dmoo@umich.edu}          %% \email is recommended
